Inter-task effects lead to an unexpected bias in human computation

### 2014-06-09 docs/publications/2014.05_PNAS/manuscript.tex
small manuscript update and update to analysis.py

Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis, Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a cheap and fast means to engage experimental 
participants and manually annotate of datasets in a research 
setting \cite{snow2008cheap}.  
Tasks involving qualitative
judgment (e.g. flagging inappropriate images), natural language annotation,
and object recognition are commonplace, since it is difficult to achieve 
comparable performance using only computers \cite{yuen2011survey}.
%Generally the worker is first given some orientation to the task, and then 
%performs the task repeatedly (e.g. label several images, one after 
%the other).

@@

To characterize such effects, we present a novel  
\textit{algorithmic definition of priming}, and a corresponding method for
measuring priming effects using machine learning algorithms.  
Traditional methods for detecting priming are of limited use in characterizing 
HPU hysteresis, because they are task-specific, and assume that priming results
in a specific class of effects.
Our approach can be applied to any task output, and does not rely on a prior 
assumption about the particular effects brought about by priming.  This 
enables the detection of priming even when the nature of the effects is not 
understood.

In the present work we investigate inter-task priming for an image-labeling 
task
on the AMT platform.  Each worker is required to label ten images featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{final set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
The final image set is always the same, but we randomly assign one of three 
initial sets, and analyze the effect this assignment has on labels attributed 
to the final set.  We employ our novel method for detecting priming effects, as
well as measuring effects on the content and specificity of attributed labels.

@@

Our purpose is different: we are interested in assessing the ramifications
that priming of HPUs could have on the processes in which they are employed.
This influences the approach we take to measurement in two ways.  First, we 
switch from focusing on the internal mechanisms of HPUs to focusing strictly 
on the HPU outputs.  Second, since we cannot \textit{a priori} know the 
application for which HPUs are being employed, we favor generality in the 
kinds of effects that can be detected.  We would like to measure any effects
that could in principle impact the application.  These considerations motivate
us to define priming effects in terms of algorithmic distinguishability of 
the output.

>>>>

Microtask crowdsourcing platforms like Amazon Mechanical Turk (AMT) make it 
possible to submit batches of small tasks to a large pool of human workers, 
who do the tasks for fun, a sense of purpose, and remuneration 
\cite{kazai2013analysis, Antin20122925}.  
Originally used to distribute clerical work, these platforms 
increasingly serve as a cheap and fast means to engage experimental 
participants and manually annotate datasets in a research 
setting \cite{snow2008cheap}.  
Tasks involving qualitative
judgment (e.g. flagging inappropriate images), natural language annotation,
and object recognition are commonplace, since it is difficult to achieve 
comparable performance using only computers \cite{yuen2011survey}.
%Generally the worker is first given some orientation to the task, and then 
%performs the task repeatedly (e.g. label several images, one after 
%the other).

@@

To characterize such effects, we present a novel  
\textit{algorithmic definition of priming}, and a corresponding method for
measuring priming effects using machine learning algorithms.  
Traditional methods for detecting priming are of limited use in characterizing 
HPU hysteresis, because they are task-specific, and assume that priming results
in a specific class of effects.
Our approach can be applied to any task output, and does not rely on prior 
assumptions about the particular effects brought about by priming.  This 
enables the detection of priming even when the nature of the effects is not 
understood.

In the present work, we investigate inter-task priming for an image-labeling 
task
on the AMT platform.  Each worker is required to label ten images featuring 
food and culture.  We regard these images as being made up of an 
\textit{initial} and \textit{final set}, but, crucially, there is no
distinction made between these sets, nor any interruption in the flow of tasks 
from the view of the worker.
The final image set is always the same, but we randomly assign one of three 
initial sets, and analyze the effect this assignment has on labels attributed 
to the final set.  We employ our novel method for detecting priming effects, as
well as measuring effects on the content and specificity of attributed labels.

@@

Our purpose is different: we are interested in assessing the ramifications
that priming of HPUs could have on the applications to which they are employed.
This influences the approach we take to measurement in two ways.  First, we 
switch from focusing on the internal mechanisms of HPUs to focusing strictly 
on the HPU outputs.  Second, we cannot \textit{a priori} know the 
application for which HPUs are being employed, but we would like to measure 
any effects that could in principle impact the application.  These 
considerations motivate us to define priming effects in terms of the 
algorithmic distinguishability of primed output.
